---
title: "Final Project on Loneliness"
author: "Frederikke Hæsum"
date: "12/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal 
I want to be able to analyse my own dataset that I created via Google Forms and cleaned up using OpenRefine. I will therefore focus mainly on creating visuals by using RStudio. 

# Getting set up 
First, I will create a few subdirectories where I can store my visuals and, potentially, any altered data. 

```{r}
dir.create("data")
dir.create("data_output")
dir.create("fig_output")
```

Now, I will load tidyverse, which contains a number of packages that I will need for my analysis. 

```{r}
library("tidyverse")
```

# Loading the data 
Next I am going to load my dataset by using the function read_csv 

```{r}
responses <- read_csv("data/Loneliness-clean-data.csv.csv")
```

I check the content of my data by using the view function, head function, or by simply typing the name of the data frame - responses - in the console:
```{r}
view(responses)
head(responses)
responses
`````

# Analysing my data
Now that I am happy with the data that has been loaded correctly, I will move on to analyse the data via visualisations. 

The respondents were asked whether they had been infected with COVID-19 or not. In order to see how the answers are distributed. I will do this by using plot function: 

```{r}
## create a vector from the data frame column "infected_with_covid"
infected_with_covid <- responses$infected_with_covid
## convert it into a factor
infected_with_covid <- as.factor(infected_with_covid)
## let's see what it looks like
infected_with_covid
```
```{r}
plot(infected_with_covid)
```

In order to make a proper visualisation I will need the ggplot2 package - it is already installed in the tidyverse package. 

## Infected with COVID-19

```{r}
responses %>%
    ggplot(aes(x = infected_with_covid)) +
    geom_bar()
```

This shows a vast amount of people not being infected at any point.

I will save this visual for later use: 
```{r}
visual_1 <- responses %>% 
  ggplot(aes(x = infected_with_covid)) +
    geom_bar() +
  labs(title = "Infected with COVID-19",
       x = "Yes or no",
       y = "Amount of respondents")
ggsave("fig_output/infectedwithcovid.png", visual_1, dpi = 500)
```
The visual will now be located in the fig_ouput directory. 

## Tendencies relating to loneliness during the pandemic
I want to look at how the different groups of respondents in terms of age, gender, and occupation have distributed their answers: 

First, I will see how the different age groups are divided - I will use the same plot function as before: 

```{r}
respondent_age <- responses$respondent_age
respondent_age <- as.factor(respondent_age)
respondent_age
```
```{r}
plot(respondent_age)
```

This shows me that the majority of the respondents are situated in the age groups 15-25 and 25-35. 

However, I will create a visual that illustrates how each individual age group have answered the question of influence on their social life. I will also put gender into the visual: 

```{r}
responses %>% 
   ggplot(aes(x = respondent_age , y = influence_on_social_life, color = respondent_gender)) +
   geom_count()
```

I am saving the visual: 

```{r}
visual_2 <- responses %>% 
  ggplot(aes(x = respondent_age , y = influence_on_social_life, color = respondent_gender)) +
   geom_count() +
  labs(title =  "Influence on social life", x = "Respondent age",
       y = "Impact on social life")

ggsave("fig_output/impactonsociallife.png", visual_2, dpi = 500)
```

## Comparison of before and during the pandemic

Now, I want to make a visual that can show me, whether or not the respondents felt more lonely before or during the pandemic:

I want to create the plot showing the difference between before and during the pandemic: 
```{r}
responses %>% 
  ggplot(aes(x = feeling_lonely_extent)) +
  geom_bar()
```

This shows the feeling of loneliness during the pandemic - I want to see what the respondents answered in terms of before the pandemic: 

```{r}
responses %>% 
  ggplot(aes(x = feeling_lonely_before_pandemic)) +
    geom_bar()
```

I am saving the two visuals for later use: 

```{r}
visual_3 <- responses %>% 
  ggplot(aes(x = feeling_lonely_extent)) +
  geom_bar() +
  labs(title =  "Feeling lonely during pandeic", x = "Extent",
       y = "Amount of respondents")

ggsave("fig_output/feelinglonelyduringpandemic.png", visual_3, dpi = 500)
```

```{r}
visual_4 <- responses %>% 
  ggplot(aes(x = feeling_lonely_before_pandemic)) +
  geom_bar() +
  labs(title =  "Feeling lonely before pandeic", x = "Extent",
       y = "Amount of respondents")

ggsave("fig_output/feelinglonelybeforepandemic.png", visual_4, dpi = 500)
```

Lastly, I want to make a visual that shows what the individual occupation groups have answered as well as marital status. 

```{r}
responses %>% 
   ggplot(aes(x = respondent_occupation , y = feeling_lonely_extent, color = marital_status)) +
   geom_count()
```

I am saving the visual: 

```{r}
visual_5 <- responses %>% 
   ggplot(aes(x = respondent_occupation , y = feeling_lonely_extent, color = marital_status)) +
   geom_count() +
  labs(title =  "Respondents marital status and occupation", x = "Occupation",
       y = "Extent of loneliness")
ggsave("fig_output/respondentsmaritalstatus_and_occupation.png", visual_5, dpi = 500)
```





