---
title: "Scraping Exercise"
author: "Frederikke Hæsum"
date: "11/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 2.2
Use the 'rvest' library to scrape data of your interest (football statistics in Wikipedia? global population by country in https://www.worldometers.info/world-population/population-by-country/ )

```{r}
library("rvest")
library("dplyr")
library("tidyr")
library("stringr")
library("janitor")
```

# Scraping website and extracting the HTML table

```{r}
url <- "https://www.worldometers.info/world-population/population-by-country/"
# scrape the website
url_html <- read_html(url)
```

```{r, option3}
whole_table <- url_html %>%
  html_nodes("table") %>%
  html_table()

head(whole_table)
```

```{r htmltodf}
new_table <- do.call(cbind,unlist(whole_table, recursive = FALSE)) 
head(new_table)
```
The line above takes the downloaded html table, unlists it and and then combine the individual elements as columns. 

## Cleaning scraped data
I am cleaning up the data with tibble, which indicates the type of data included in each column as listed in an abbreviated fashion below the column names

```{r}
mastertable <- new_table
mastertable <- as_tibble(mastertable)
str(mastertable)
```

## Write result to file

I'm exporting the data to a file like so: 

```{r}
data <- mastertable 
write.csv(data,"data/populationbycountry.csv")
```

